
\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\author{Mircea Grecu and William S. Olson}
\title{Satellite Combined Radar-Radiometer
algorithms\\
Responses to Reviewer 2}
\date{}
\begin{document}
\maketitle


We thank the reviewer for the insightful comments and suggestions. 
Here are our point by point responses.

\begin{enumerate}
    \item{\textit{p.2, 4th line of the 2nd paragraph: “This because” $\rightarrow$ "This is because"}\\
    Thank you for pointing this out.  We have corrected it in the text.
    }
    \item{\textit{p.3, below Eq. (1.1): When the inequality ...}\\
    We have corrected as suggested.
    }
    \item{\textit{p.4 and others: Sometimes, the reference number does not appear in order.}\\
    Thank you for pointing this out.  We reordered the references.
    }
    \item{\textit {p.7, 1st line: dNw reminds me of the deviation of Nw from the standard value as if dNw = Nw-Nw0. 
    It may be better to use different notation to show the ratio between Nw and Nw0.}\\
    Thank you for the suggestion. We agree, changed $dN_w$ to $N_{w,rel}$.
    }
    \item{\textit{p.7, 3rd line from the bottom: This is just a comment, but a factor f is equivalent with epsilon}\\
    Thank you for the comment. We included a comment in the text regarding this.
    }
    \item{\textit{p.13, 2nd line of the 2nd paragraph: (GMP) $\rightarrow$ (GPM).}\\
    Thank you for pointing this out.  We have corrected it in the text.
    }
    \item{\textit{p.13, 2nd line of the 2nd paragraph: shown in 1.2.4.1 $\rightarrow$ Fig. 1.2,
    p. 14, 1st line of the last paragraph: figure 1.3.1 $\rightarrow$ Fig. 1.3. Hereafter, the figure numbers need to be corrected.}\\
    We apologize for the incorrect labeling. We believe it is caused by the Latex supporting files that were provided by the publisher. 
    We refer to figures in the text using labels rather than numbers, and rely on the Latex compiler to assign the correct numbers to the figures.
    The style file provided by the publisher does not seem to work properly on our system, but we believe the professional editor can easily fix the
    figure numbering problem during the editorial process.
    }
    \item{\textit{p.14, 1st line of the last paragraph: As “GPM” appears several times before, here it is not
    necessary to spell out the full term.}\\
    Thank you for the suggestion. We have included it in the text.
    }
    \item{\textit{p.15, 6th line from the bottom of the 1st paragraph: Please show the unit of “15.0”. The
    footprint of the radiometer is different between along scan and cross scan directions. This
    value is for which direction?}\\
    Thank you for pointing this out. The GMI's footprint size is 11 km in the along scan direction 18 km in the cross scan direction.
    We have included this information in the text.
    }
    \item{\textit{p.15, 5th line from the bottom: DPR’s footprint is not 4.5 km but 5.0 km.}\\
    Thank you for pointing this out.  We have corrected it in the text.
    }
    \item{\textit{p.17: Fig. 1.3.2 $\rightarrow$ Fig. 1.4. Hereafter, the figure numbers need to be corrected.}\\
    This is related to the aforementioned problem with the figure numbering.
    }
    \item{\textit{Figure 1.5: The top figure shows PIA at Ku-band? I think the values are too large. Particularly,
    at scan 20, SRT estimates PIA is more than 100 dB, but it is impossible to estimate such large
    PIA by SRT because of the missing of surface echo (or saturation of PIA).}\\
    The top figure shows the differential PIA, i.e. PIA(Ka)-PIA(Ku). The Ku-band based estimate PIA(Ka)-PIA(Ku) is just 5 
    times the Ku-band SRT PIA value.
    Both the single and dual-frequency estimates are considered valid in the 2ADPR file.  The sigma0 values are -14.09 and
    -31.99 dB.
    }
    \item{\textit{Figure 1.5: It is better to show the legend for the bottom figure.}\\
    Thank you for the suggestion. We added a legend for the bottom figure.
    }
    \item{\textit{Reference [2]: This work was published in 1954, not 1990.}\\
    Thank you for pointing this out.  We have corrected it in the text.
    }

\end{enumerate}
\end{document}